\documentclass[12pt]{article}
\usepackage{fancyhdr, amsfonts, amsmath, amssymb, graphicx, color, fullpage}
\pagestyle{fancy}
\usepackage{longtable}
\usepackage{fourier}
\usepackage[lf]{venturis}
\usepackage[T1]{fontenc}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\parindent{0pt}
\usepackage{amsfonts, amsmath, amssymb, bm} %Math fonts and symbols
\usepackage{dcolumn, multirow} % decimal-aligned columns, multi-row cells
\usepackage{graphicx} % graphics commands
\usepackage{subfig}
\usepackage{float}
\usepackage[margin=1in]{geometry} % sets page layout
\usepackage{setspace}% allows toggling of double/single-spacing
\usepackage{verbatim}% defines environment for un-evaluated code
\usepackage{rotating}% defines commands for rotating text and floats
\usepackage{natbib}% defines citation commands and environments.
\usepackage{url}
\usepackage{caption}
\usepackage{endnotes}
\usepackage{psfrag}
\usepackage{epstopdf}
\usepackage{epsfig}
\usepackage[pdftex,
            pdfauthor={Tom Hanna},
            pdftitle={The Title},
            pdfsubject={The Subject},
            pdfkeywords={Some Keywords},
            pdfcreator={TeXstudio}]{hyperref}
\usepackage{outlines}
\usepackage{enumitem}
\setlist[enumerate,1]{label=\Roman*)}
\setlist[enumerate,2]{label=\Alph*)}
\setlist[enumerate,3]{label=\roman*)}
\setlist[enumerate,4]{label=\alph*)}

\setlength\parindent{0pt}
\setlength{\headsep}{0.2in}

\begin{document}
	\lhead{POLS 6481, Spring 2021}
	\chead{Lab 8 Survey}
	\rhead{Due April 13}
	
	

	
	{\textcolor{white}.}
	

	
	\section*{Part 1}
	
	\begin{enumerate}[label=\arabic*]
	 \setcounter{enumi}{8}
	\item Briefly describe a quantitative project you are working on but for which you have not completed the hypothesis testing stage. This can be a paper for another class this semester or a research design paper from last semester that you would like to move forward. This can be a semester paper or a shorter assignment as long as it involves hypothesis testing. It does not need to be a project where you will actually complete all the data work this semester. Your description should include the research question and your basic theory/main hypotheses. (One to three sentences is fine. A page is too much.)
	
	\item What are your data source(s) for the project? What are your main dependent, explanatory, and major control variables?
		
	\end{enumerate}
	
\section*{Extra Credit}
	\begin{enumerate}[label=\arabic*]
		 \setcounter{enumi}{10}
		 
	\item Describe your dependent variable specifically by type of variable and distribution. What sort of model do you intend to use (OLS, logit, probit, other)? "I need help choosing" is an acceptable answer, but in that case tell me what you think. Is there anything unusual about the distribution or correlations of the other variables?
	
	\item What would help you in the remainder of this class to complete what you need for this project?
	
	\end{enumerate}
	


\end{document}
